---
title: "TrajDataMining"
author: "Diego Monteiro"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TrajDataMining}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## TrajDataMining

A new method to detect a pattern called Partners in trajectories. This algorithm identifies pairs of trajecories whose objects saty together during certain
periods. This method is avaliable in the TrajDataMining package. It differs
from existing moving together patterns because its implementation is highly
parallelizable and its clustering method is based on distance time series analysis.



## Example data gives
```{r}
library(TrajDataMining)
library(ggplot2)
library(sp)
library(magrittr)
suppressMessages(library(rgdal))
```

## Plot of A1 data example

### A1 track its a trajectory of sea elephant

```{r ,fig.height=4,fig.width=4,fig.align='center'}

  df <- data.frame(x=A1@sp@coords[,1],y=A1@sp@coords[,2])

  ggplot(df,aes(x=df$x,y=df$y))+geom_path(aes(group = 1), arrow = arrow(),color='blue')+ggtitle("elephant sea Trajectory")+xlab("X")+ ylab("Y")+theme_classic()
  
```


## Douglas Peucker Method

#### Douglas-Peucker which reduces trajectories by preserving spatial precisions.

```{r, fig.height=4,fig.width=4,fig.align='center'}

# get the maximum distance
 max <- max(A1@connections$distance)

 douglasp <- douglasPeucker(A1,max)
 
 df <- data.frame(x=douglasp@sp@coords[,1],y=douglasp@sp@coords[,2])
 ggplot(df,aes(x=df$x,y=df$y))+geom_path(aes(group = 1), arrow = arrow(),color='blue')+ggtitle("Method Douglas Peucker")+xlab("X")+ ylab("Y")+theme_classic()
 
```


## Speed Filter

#### A speed filter that filters out trajectory observations whose speeds are above a user-defined maximum velocity ( ETIENNE , 2011).

```{r, fig.height=4,fig.width=4,fig.align='center'}

# get the maximum distance
  sf <- speedFilter(A1,0.01)
  df <- data.frame(x=sf@sp@coords[,1],y=sf@sp@coords[,2])

 ggplot(df,aes(x=df$x,y=df$y))+geom_path(aes(group = 1), arrow = arrow(),color='blue')+ggtitle("Method Speed Filter")+xlab("X")+ ylab("Y")+theme_classic()
```

## Partner

#### A method, named Partner, that identifies objects that are moving together. We propose this method to recognize trajectories that stay together, based on trajectory distance time series analysis.

#### For to send this data for the database use the class DataSourceInfo.
```{r, fig.height=6,fig.width=6,fig.align='center'}
 
  data <- FALSE
  
  partner(A1,A2,110792,2277,0,data)

  

```






